Semantic browsing of sound databases \\ without keywords

### 2016-05-09 responseToReviewers.tex

\documentclass[10pt]{article}

\title{Response to Reviewers: \\ AES-D-16-00016
Semantic browsing of sound databases without keywords}

\usepackage{color}
\newcommand{\gl}[1]{\textcolor{red}{Gregoire : #1}}
\newcommand{\nm}[1]{\textcolor{magenta}{Nicolas : #1}}
\newcommand{\ml}[1]{\textcolor{blue}{ Mathieu : #1}}

\begin{document}

\maketitle

We would like to thank the editor and the reviewers for their comments and suggestions. Following these comments, we made several changes to the article, which are summarized here. The next sections list our answers to each of the reviewer’s comments, with references to the revised manuscript where appropriate.

\ml{TODO: put analysis data online, and website}

\section{Responses to Reviewer 1}

\begin{enumerate}

\item \emph{}

\end{enumerate}

\section{Responses to Reviewer 2}

\begin{enumerate}

\item \emph{}

\end{enumerate}

\section{Full text}

Reviewer 1: This paper proposes a new method for navigating environmental sound libraries using a constrained and unconstrained display that visualises semantic organisation of sounds. The authors build and evaluate two interfaces for navigation and compare them to a baseline method in which sounds are arranged in a 2D space using on MFCC based distances mapped to two dimensions using multi dimensional scaling. The semantic grouping in contrast are based on a hierarchical structure of conceptual/cognitive relatedness that is manually annotated. The assessment looks at search efficiency in absolute terms using information collected during user studies, including search time and the number of sounds a user had to listen to before reaching a target sound. The evaluation also looks at how efficiency changes over time as users become more familiar with the interface.

The idea is relatively novel and clearly presented, the collected data is valuable and subjected to appropriate statistical validation. There are clear conclusions drawn from this. For these reasons I recommend the paper to be published after minor editorial changes and clarifications.

The only question regarding the technical content that wasn't entirely clear to me is whether the sounds heard counter was reset for each search? That is, wehther the total and unique heard sounds are related to the whole experiment or an average value per target? How many target sounds were assessed by each subject? Was this controlled by the study or was the study simply time limited? Perhaps in the post-hoc analyses it would be useful to know if FSD produces significant results in pair-wise tests with Bonferroni correction (since this is, albeit simple, still a multiple comparison test).

Typos:
On page 5, Section 5.2  "...the three metrics are presented on Figure 6. " => should be in Figure 6.

Reviewer 2: Any additional comments you write here will be available to the author. You may also upload an annotated manuscript and/or detailed comments file.

The authors describe some user experiments investigating the use of semantic organization for visual browsing of sound databases without keywords. 
The main idea is to display the hierarchical organization of the data to facilitate browsing. Overall the paper is well written and easy to understand. The 
experimental methodology is good and the results support the conclusions with some caveats that I mention below. The bibliography is good but 
could be improved with some more recent references in music browsing. I think it will make a good contribution to the special issue especially 
if one or more of the following suggestions are addressed by the authors - they are not essential but I think they would make the paper 
much stronger and help it have more impact. Currently it reads like a strong conference paper but a weak journal article. 
My suggestions are:

1) The title is misleading i.e sound databases is too general and could encompass music, speech such oral histories, sound effects, bio-acoustic signals etc. 
The assumption that the findings generalize to other types of sound is too far stretched as for example music and urban sound are extremely different 
in how they are perceived organized by listeners. I would prefer a more honest title such as:

Semantic browsing of urban envrionment sounds without keywords

If the author replicate the same experiment for example using a music collection or a collection of bird songs and the findings were consistent 
this would justify the old title (and make the paper much stronger)

2) The references are relatively old. There have been several newer efforts to develop browsing interfaces especially in the music domain. 
For example the Musicream, Musicrainbow and Musicsun interfaces. 
Knees, Peter, et al. "An innovative three-dimensional user interface for exploring music collections enriched." Proceedings of the 14th annual ACM international conference on Multimedia. ACM, 2006.
Lillie, Anita Shen. MusicBox: Navigating the space of your music. Diss. Massachusetts Institute of Technology, 2008.

3) The uses of Kruskal's normalized stress is interesting but raises the concern that the hierarchical organization improvement might be specific to this approach. It would have been 
really good to have a few other ways to map the audio features to a spatial display (the classic PCA for example or SOM) and then compare the different interfaces. I realize that 
this would require more extensive experiments but it would make the paper much stronger.

4) Finally even though I agree with some of the arguments for avoiding keywords as a way of searching they can be used to help the user understand the space. Even some thing 
as simple as showing the word associated with a category when navigating would probably help. This would be an easy configuration to test and I am surprised the authors 
have done so. I suspect that the speed and efficiency would improve.

\end{document}

### 2016-05-31 responseToReviewers.tex

\section{Responses to Reviewer 1}

\gl{do it}

\begin{enumerate}

\item \emph{[Are] the sounds heard counter was reset for each search? That is, whether the total and unique heard sounds are related to the whole experiment or an average value per target?}

\item \emph{How many target sounds were assessed by each subject?}

\item \emph{Was this controlled by the study or was the study simply time limited?}

\item \emph{Perhaps in the post-hoc analyses it would be useful to know if FSD produces significant results in pair-wise tests with Bonferroni correction (since this is, albeit simple, still a multiple comparison test).}

\item \emph{On page 5, Section 5.2  "...the three metrics are presented on Figure 6. " => should be in Figure 6.}

This typo is now fixed.

@@

\end{enumerate}

\section{Responses to Reviewer 2}

\begin{enumerate}

\item \emph{If the author replicate the same experiment for example using a music collection or a collection of bird songs and the findings were consistent 
this would justify the old title (and make the paper much stronger)}

This is an excellent suggestion that we decided to do by considering an alternative dataset of sounds produced by musical instruments. As shown on Section 6 of the updated paper, the findings are consistent with the ones obtained using the urban sound dataset.

We thus keep the original title.

\item \emph{The references are relatively old. There have been several newer efforts to develop browsing interfaces especially in the music domain. 
For example the Musicream, Musicrainbow and Musicsun interfaces. 
Knees, Peter, et al. "An innovative three-dimensional user interface for exploring music collections enriched." Proceedings of the 14th annual ACM international conference on Multimedia. ACM, 2006.
Lillie, Anita Shen. MusicBox: Navigating the space of your music. Diss. Massachusetts Institute of Technology, 2008.}

Those references are added to the previous work (Section 1).

\item \emph{The uses of Kruskal's normalized stress is interesting but raises the concern that the hierarchical organization improvement might be specific to this approach. It would have been 
really good to have a few other ways to map the audio features to a spatial display (the classic PCA for example or SOM) and then compare the different interfaces.}

We agree that more extensive research should be done regarding the type of features used and the type of projection used. We originally chose the MDS as it has better performance than the PCA and have the advantage of not relying on any parameter setting unlike the SOM approach.

This latter motivation is added to the manuscript in Section 3.

Comparing to an optimized SOM display would have been interested, along with the use of other features. That said, we decided to dedicate the complementary experiments to the use of an alternate dataset.

\item \emph{some thing 
as simple as showing the word associated with a category when navigating would probably help. This would be an easy configuration to test and I am surprised the authors [not]
have done so. I suspect that the speed and efficiency would improve.
}

We agree that this configuration would have helped us gaining a more precise understanding of the results. However, we chose to focus our study on completely non verbal displays as stated in the introduction.

Even if this complementary study would have increase the level of knowledge, we decided to focus the complementary experiments to the use of an alternative dataset.

### 2016-05-31 lafaySsf2016.tex
nico names
preparing v2

\usepackage{color,url}
\newcommand{\gregoire}[1]{\textcolor{red}{Gregoire : #1}}
\newcommand{\mathias}[1]{\textcolor{green}{Mathias : #1}}
\newcommand{\ml}[2][]{\textcolor{blue}{#1 #2}}

@@

%Author Info.
\authorgroup{
\author{Gr\'egoire Lafay$^1$}, \author{Nicolas Misdarris$^2$},
\author{Mathieu Lagrange$^1$}, \author{Mathias Rossignol$^2$}
\email{(gregoire.lafay@irccyn.ec-nantes.fr)}
\affil{IRCCyN, Ecole Centrale de Nantes $^1$ \quad\quad\quad\quad IRCAM, STMS, UPMC $^2$}
}

@@

%% A category with the (minimum) three required fields
%\category{H.2.8}{Database Management}{Database Applications}[Data mining]
%%%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

%\terms{Design, Experimentation, Human Factors}

@@

\begin{enumerate}
\item Sounds, as many others things, can be described in many ways. Sound may be designated by their
sources (a car door), as well as by the action of those sources (the slamming of a car door) or their environments (slamming a car door in a garage) \cite{houix2012lexical, niessen2010categories, brown2011towards}. Designing an effective keyword-based search system requires an accurate description of each sound, which has to be tunable to the sound representation of each user.
\item Pre-defined verbal descriptions of the sounds made available to the users may potentially bias their browsing and final selection.
\item Localization of the query interface is made difficult as the translation of some words referring to qualitative aspects of the sound, such as its ambience, is notoriously ambiguous and subject to cultural specificities.
\item Unless considerable time and resources are invested into developing a multilingual interface, any system based on verbal descriptions can only be used with reduced performance by non-native speakers of the chosen language.
\end{enumerate}
To circumvent those issues, not relying on keywords is desirable. However, conveying semantics remains a necessity for ease of browsing, which raises the question of what alternate means, other than written language, can be used to that end.

@@

Most of the research effort in the sound design and Music Information Retrieval (MIR) communities is focused on acoustical based indexing and browsing \cite{tzanetakis2003musescape, streich2008music}. Typically, the items (sound effects or pieces of music) are modeled by processing the digital audio waveform through some signal processing pipeline in order to get a compact description of each item
\cite{coleman2007mused}. Then, statistical projections or embedding techniques, like Principal Components Analysis (PCA),  Multi Dimensional Scaling (MDS) \cite{schwarz2009sound,Cano2002}, Self Organizing Maps (SOM) \cite{pampalk2004exploring} and the like are used to project the items in a two or three dimensional space while preserving as much as possible the distances among them. One of the advantages of such an approach is its ability to scale to very large databases \cite{schwarz2009scalability} as it does not need any kind of manual annotation and allows the user to search by similarity efficiently according to acoustical properties.

@@

\section{Dataset} \label{dataset}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.24]{gfx/SSF.pdf} 
\end{center}
\caption{\label{figSSF} Semantic displays are  based on the semantic hierarchical structure of the dataset.}
\end{figure}

The dataset considered in this study is composed of 149 urban environmental sound events. Its semantic organization is as follows: a sound is characterized by a tag describing the physical source of the sound (\textit{man-yelling}, \textit{car-passing}). Sounds are then hierarchically grouped into classes according to their tags (\textit{car} $>$ \textit{car-passing}; \textit{car} $>$ \textit{car-starting}). Those classes are in turn packed into classes until high level classes describing broader concepts are reached (\textit{traffic} $>$ \textit{car} $>$ \textit{car-passing}). The sound dataset is thus organized into a hierarchical structure of semantic classes as described in Figure~\ref{figdataset}. Strictly speaking, the sound samples of the dataset are the leaf semantic levels. All the other classes are represented by a \textit{prototype sound} that best characterizes the sounds belonging to the class.

@@

@@

As a reference, an Acoustic Display (AD) provides a spatial representation based on acoustic descriptors. Each sound is described by time-averaged Mel-Frequency Cepstrum Coefficients (MFCCs) computed with standard parameter settings (13 lowest quefrency coefficients are kept out of 40). The Euclidean distance between time averaged features is then computed for each sound pair. A non metric multidimensional scaling with Kruskal's normalized stress \cite{kruskal1964multidimensional} is then employed to project the data into two dimensions according to this distance, see Figure \ref{figXP3}.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.18]{gfx/xp3.png} 
\end{center}
\caption{\label{figXP3} Acoustical Display (AD).}
\end{figure}

Two semantically oriented displays are then proposed, called Full Semantic Display (FSD) and Progressive Semantic Display (PSD), shown on Figures~\ref{figXP2} and~\ref{figXP1}, respectively. Both display  consider the hierarchical structure of the dataset to organize sounds. Each sound class is represented by a filled circle. Circles are then packed together according to the hierarchical semantic organization of the dataset, as shown on Figure~\ref{figSSF}. Thus, subclasses belonging to the same class are close to each others. Circle packing functions of the D3.js (Data-Driven Documents) javascript library \cite{2011-d3} are used to distribute the sound classes in the space. Depending on the display, the user can either access each leaf class directly, or has to click through intermediate levels of the hierarchy.

More precisely, with the FSD display, users can directly visualize the whole hierarchy, down to the leaf classes, while with the PSD display, users only have access, at first, to the intermediate semantic levels of the hierarchy. Upon first using PSD, they observe circles representing the top classes of the semantic hierarchical structure of the dataset. When users click on a circle, they hear the sound prototype of the class and the subclasses are progressively revealed, represented by white circles contained in the circle that has just been clicked. The same action repeats itself until the user reaches the leaf classes of the hierarchy. The leaf classes are represented with small gray circles, indicating that there is no subclass to uncover. Thus the PSD has a constrained exploration system. Each time a sub-circle is automatically revealed, its sound prototype is played. Users may stop the discovery process by clicking on an other circle. In this display, the leaf classes are distributed  in the same manner as FSD. Thus, the spatial configuration of the unfolded version of PSD, which may be obtained after discovering all the classes and subclasses, is equivalent to the one of FSD, as shown on Figures~\ref{figXP2}, \ref{figXP1} and \ref{figSSF}.

@@

\begin{figure}[t!]
\begin{center}
\includegraphics[scale=0.30]{gfx/XP2clean.pdf} 
\end{center}
\caption{\label{figXP2} Full Semantic Display (FSD): implicit hierarchical organization of semantic classes.}
\end{figure}

\begin{figure*}[t]
\begin{center}
\includegraphics[scale=0.4]{gfx/XP1clean2.pdf} 
\end{center}
\caption{\label{figXP1} Progressive Semantic Display (PSD):  explicit hierarchical organization of semantic classes. (a) initial folded version; (b) partly folded version; (c) unfolded version.}
\end{figure*}

\section{Experiment} \label{test}

@@

During this experiment, the three displays are compared. By comparing AD and xSD (the two semantic displays), the goal is to evaluate the  relative efficiencies of semantic based and acoustic based spatial configurations. By comparing FSD and PSD, we study the impact of an enforced hierarchical exploration of the corpus by the user. The goal is to check if constraining the user to first browse the high levels of the hierarchy helps him to grasp and memorize the spatial configuration and the organization of the sound classes.

@@

We evaluate and compare those three displays with a crowdsourcing web-based experiment \footnote{The test is available at \url{http://soundthings.org/research/speedSoundFinding/index.html}, each of the 3 displays is also available by appending a digit from 1 to 3 to \textit{index} in the above cited url.} for which we adopt a between subject approach, \textit{i.e.} a subject can only test one display. In this experiment, subjects are asked to successively retrieve 13 target sounds among the 149 of the whole dataset. The target sounds are selected such that there are at least two target sounds in each top-level class of the semantic hierarchical structure of the dataset. To reduce order effects, target sounds are presented to each subject in random order.

@@

60 subjects have completed the experiment, 20 for each interface.

@@

\section{Results} \label{results}

\subsection{Outlier detection}

\begin{table}[t]
\caption{\label{tab1} Criterion used to detect outliers.}
\begin{center}
\begin{tabular}{ccccc}
criterion      &  1  &  2  &  3  &  4  \\
\hline
outlier 1 (PD) & --- & --- & --- &  x  \\
outlier 2 (PD) &  x  & --- & --- & --- \\  
outlier 3 (AD) & --- & --- & --- &  x \\
outlier 4 (AD) &  x  &  x  &  x  & --- \\
outlier 5 (AD) &  x  & --- & --- & --- \\
\hline
\end{tabular}
\end{center}
\end{table}

Using the $IQR$ method, 5 subjects are detected as outliers and removed from the analysis. 2 of those subjects used PD and 3 subjects AD. Table~\ref{tab1} shows the criteria used to detect the 5 outliers. 3 subjects are detected by considering the \textit{absolute duration}. They spent respectively 50 minutes, 5 hours and 17.5 hours to complete the experiment. 1 subject is detected by considering the total search duration (46 minutes), and an other by observing the total number of heard sounds (1800 heard sounds, roughly 12 times the total size of the corpus). And lastly 2 subjects are detected by observing the maximum number of times they had to hear a target sound before finding it (4 and 8 times).

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{gfx/analyse1.eps} 
\end{center}
\caption{\label{fig1} Average and standard deviation for (a) the total search durations, (b) the number of heard sounds and (c) the number of unique heard sounds.}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{gfx/analyse2.eps} 
\end{center}
\caption{\label{fig2} evolution of (a) the average search durations, (b) the average numbers of heard sounds, and (c) the average numbers of unique heard sounds at each target sound search. Lines are linear regression fits.}
\end{figure}

@@

The averages and standard deviations for the three metrics are presented on Figure~\ref{fig1}. The type of display has a significant effect on the the \textit{total search duration} ($F[2,52]=3.63; p=0.03$), the number of heard sounds ($F[2,52]=5.65; p<0.01$) and the number of unique heard sounds ($F[2,52]=8.65; p<0.01$). Post hoc analysis on the total search time (Figure~\ref{fig1}~(a)) shows that FSD performs better than the other interfaces (FSD-PSD: $p=0.04$; FSD-AD: $p=0.02$), whereas PSD and AD seem to have similar results (PSD-AD: $p=0.88$).

@@

\subsection{Learning phenomenon}

@@

>>>>

\usepackage{color,url}
\newcommand{\gl}[1]{\textcolor{red}{Gregoire : #1}}
\newcommand{\mr}[1]{\textcolor{green}{Mathias : #1}}
\newcommand{\ml}[2][]{\textcolor{blue}{#1 #2}}

@@

%Author Info.
\authorgroup{
\author{Gr\'egoire Lafay$^1$}, \author{Nicolas Misdariis$^2$},
\author{Mathieu Lagrange$^1$}, \author{Mathias Rossignol$^2$}
\email{(gregoire.lafay@irccyn.ec-nantes.fr)}
\affil{IRCCyN, Ecole Centrale de Nantes $^1$ \quad\quad\quad\quad IRCAM, STMS, UPMC $^2$}
}

@@

@@

\begin{enumerate}
\item Sounds, as many others things, can be described in many ways. Sound may be designated by their
sources (a car door), as well as by the action of those sources (the slamming of a car door) or their environments (slamming a car door in a garage) \cite{houix2012lexical, niessen2010categories, brown2011towards}. Designing an effective keyword-based search system requires an accurate description of each sound, which has to be tunable to the sound representation of each user.
\item Pre-defined verbal descriptions of the sounds made available to the users may potentially bias their browsing and final selection.
\item Localization of the query interface is made difficult as the translation of some words referring to qualitative aspects of the sound, such as its ambiance, is notoriously ambiguous and subject to cultural specificities.
\item Unless considerable time and resources are invested into developing a multilingual interface, any system based on verbal descriptions can only be used with reduced performance by non-native speakers of the chosen language.
\end{enumerate}
To circumvent those issues, not relying on keywords is desirable. However, conveying semantics remains a necessity for ease of browsing, which raises the question of what alternate means, other than written language, can be used to that end.

@@

Most of the research effort in the sound design and Music Information Retrieval (MIR) communities is focused on acoustical based indexing and browsing \cite{tzanetakis2003musescape, streich2008music,goto2005musicream,pampalk2007musicsun}. Typically, the items (sound effects or pieces of music) are modeled by processing the digital audio waveform through some signal processing pipeline in order to get a compact description of each item
\cite{coleman2007mused} with sometime additional textual features. Then, statistical projections or embedding techniques, like Principal Components Analysis (PCA) \cite{MusicBox},  Multi Dimensional Scaling (MDS) \cite{schwarz2009sound,Cano2002}, Self Organizing Maps (SOM) \cite{pampalk2004exploring,pampalk2006musicrainbow,knees2006innovative} and the like are used to project the items in a two or three dimensional space while preserving as much as possible the distances among them. One of the advantages of such an approach is its ability to scale to very large databases \cite{schwarz2009scalability} as it does not need any kind of manual annotation and allows the user to search by similarity efficiently according to acoustical properties.

@@

\section{Datasets} \label{dataset}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.24]{gfx/SSF.pdf} 
\end{center}
\caption{\label{figSSF} Semantic displays are  based on the semantic hierarchical structure of the dataset. \gl{generate an alternative bw figure}}
\end{figure}

The datasets considered in this study are respectively composed of 149 urban environmental sound events and 137 musical sounds produced by musical instruments.

The former has a semantic organization as follows: a sound is characterized by a tag describing the physical source of the sound (\textit{man-yelling}, \textit{car-passing}). Sounds are then hierarchically grouped into classes according to their tags (\textit{car} $>$ \textit{car-passing}; \textit{car} $>$ \textit{car-starting}). Those classes are in turn packed into classes until high level classes describing broader concepts are reached (\textit{traffic} $>$ \textit{car} $>$ \textit{car-passing}). The sound dataset is thus organized into a hierarchical structure of semantic classes as described in Figure~\ref{figdataset}. Strictly speaking, the sound samples of the dataset are the leaf semantic levels. All the other classes are represented by a \textit{prototype sound} that best characterizes the sounds belonging to the class.

@@

Similarly, the latter also has a semantic organization \gl{describe music dataset}

@@

As a reference, an Acoustic Display (AD) provides a spatial representation based on acoustic descriptors. Each sound is described by time-averaged Mel-Frequency Cepstrum Coefficients (MFCCs) computed with standard parameter settings (13 lowest quefrency coefficients are kept out of 40). The Euclidean distance between time averaged features is then computed for each sound pair. A non metric multidimensional scaling (MDS) with Kruskal's normalized stress \cite{kruskal1964multidimensional} is then employed to project the data into two dimensions according to this distance, see Figures \ref{figXP3urban} \ref{figXP3music}. The latter exhibit a clear distinction between percussive (left) and sustained sounds (right).

Among the several alternative that exists, MFCCs features are considered as they are widely used in the audio processing community. The MDS is selected as it has lower sensitivity to outliers than the PCA and have the advantage of not relying on any parameter setting unlike the SOM approach.

%\begin{figure}[t]
%\begin{center}
%\includegraphics[scale=0.18]{gfx/xp3.png} 
%\end{center}
%\caption{\label{figXP3} Acoustical Display (AD).}
%\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.5\textwidth]{gfx/urban_mds.png} 
\end{center}
\caption{\label{figXP3urban} Acoustical Display for the urban sound dataset (AD). Colors and legend are removed during the experiment.}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.5\textwidth]{gfx/music_mds.png} 
\end{center}
\caption{\label{figXP3music} Acoustical Display for the musical sound dataset (AD). Colors and legend are removed during the experiment.}
\end{figure}

Two semantically oriented displays are then proposed, called Full Semantic Display (FSD) and Progressive Semantic Display (PSD)%, shown in Figures~\ref{figXP2} and~\ref{figXP1}, respectively. 
Both display  consider the hierarchical structure of the dataset to organize sounds. Each sound class is represented by a filled circle. Circles are then packed together according to the hierarchical semantic organization of the dataset, as shown in Figure~\ref{figSSF}. Thus, subclasses belonging to the same class are close to each others. Circle packing functions of the D3.js (Data-Driven Documents) javascript library \cite{2011-d3} are used to distribute the sound classes in the space. Depending on the display, the user can either access each leaf class directly, or has to click through intermediate levels of the hierarchy.

More precisely, with the FSD display, users can directly visualize the whole hierarchy, down to the leaf classes, while with the PSD display, users only have access, at first, to the intermediate semantic levels of the hierarchy. Upon first using PSD, they observe circles representing the top classes of the semantic hierarchical structure of the dataset. When users click on a circle, they hear the sound prototype of the class and the subclasses are progressively revealed, represented by white circles contained in the circle that has just been clicked. The same action repeats itself until the user reaches the leaf classes of the hierarchy. The leaf classes are represented with small gray circles, indicating that there is no subclass to uncover. Thus the PSD has a constrained exploration system. Each time a sub-circle is automatically revealed, its sound prototype is played. Users may stop the discovery process by clicking on an other circle. In this display, the leaf classes are distributed  in the same manner as FSD. Thus, the spatial configuration of the unfolded version of PSD, which may be obtained after discovering all the classes and subclasses, is equivalent to the one of FSD, as shown in Figures~\ref{figXP2}, \ref{figXP1} and \ref{figSSF}.

@@

%\begin{figure}[t!]
%\begin{center}
%\includegraphics[scale=0.30]{gfx/XP2clean.pdf} 
%\end{center}
%\caption{\label{figXP2} Full Semantic Display (FSD): implicit hierarchical organization of semantic classes.}
%\end{figure}
%
%\begin{figure*}[t]
%\begin{center}
%\includegraphics[scale=0.4]{gfx/XP1clean2.pdf} 
%\end{center}
%\caption{\label{figXP1} Progressive Semantic Display (PSD):  explicit hierarchical organization of semantic classes. (a) initial folded version; (b) partly folded version; (c) unfolded version.}
%\end{figure*}

\section{Experiments} \label{test}

@@

During this experiment, the three displays are compared using two corpora: the urban sound corpus and the musicla sound corpus. By comparing AD and xSD (the two semantic displays), the goal is to evaluate the  relative efficiencies of semantic based and acoustic based spatial configurations. By comparing FSD and PSD, we study the impact of an enforced hierarchical exploration of the corpus by the user. The goal is to check if constraining the user to first browse the high levels of the hierarchy helps him to grasp and memorize the spatial configuration and the organization of the sound classes.

@@

We evaluate and compare those three displays with a crowdsourcing web-based experiment \footnote{The tests are available at \url{http://soundthings.org/research/speedSoundFinding/index.html} and \url{http://soundthings.org/research/speedSoundFindingMusic/index.html}, each of the 3 displays is also available by appending a digit from 1 to 3 to \textit{index} in the above cited url.} for which we adopt a between subject approach, \textit{i.e.} a subject can only test one display. In this experiment, subjects are asked to successively retrieve 13 target sounds among the whole dataset. The target sounds are selected such that there are at least two target sounds in each top-level class of the semantic hierarchical structure of the dataset. To reduce order effects, target sounds are presented to each subject in random order.

@@

60 subjects have completed the experiment for the urban sound dataset, 20 for each interface. \ml{describe for music}

\subsection{Outliers Detection}

@@

\section{Results on Urban Sounds} \label{resultsu}

\subsection{Outliers}

%\begin{table}[t]
%\caption{\label{tab1} Criterion used to detect outliers.}
%\begin{center}
%\begin{tabular}{ccccc}
%criterion      &  1  &  2  &  3  &  4  \\
%\hline
%outlier 1 (PD) & --- & --- & --- &  x  \\
%outlier 2 (PD) &  x  & --- & --- & --- \\  
%outlier 3 (AD) & --- & --- & --- &  x \\
%outlier 4 (AD) &  x  &  x  &  x  & --- \\
%outlier 5 (AD) &  x  & --- & --- & --- \\
%\hline
%\end{tabular}
%\end{center}
%\end{table}

Using the $IQR$ method, 5 subjects are detected as outliers and removed from the analysis. 2 of those subjects used PD and 3 subjects AD. %Table~\ref{tab1} shows the criteria used to detect the 5 outliers. 
3 subjects are detected by considering the \textit{absolute duration}. They spent respectively 50 minutes, 5 hours and 17.5 hours to complete the experiment. 1 subject is detected by considering the total search duration (46 minutes), and an other by observing the total number of heard sounds (1800 heard sounds, roughly 12 times the total size of the corpus). And lastly 2 subjects are detected by observing the maximum number of times they had to hear a target sound before finding it (4 and 8 times).

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{gfx/analyse_urban1.eps} 
\end{center}
\caption{\label{fig1} Average and standard deviation for (a) the total search durations, (b) the number of heard sounds and (c) the number of unique heard sounds.}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{gfx/analyse_urban2.eps} 
\end{center}
\caption{\label{fig2} evolution of (a) the average search durations, (b) the average numbers of heard sounds, and (c) the average numbers of unique heard sounds at each target sound search. Lines are linear regression fits.}
\end{figure}

@@

The averages and standard deviations for the three metrics are presented in Figure~\ref{fig1}. The type of display has a significant effect on the the \textit{total search duration} ($F[2,52]=3.63; p=0.03$), the number of heard sounds ($F[2,52]=5.65; p<0.01$) and the number of unique heard sounds ($F[2,52]=8.65; p<0.01$). Post hoc analysis on the total search time (Figure~\ref{fig1}~(a)) shows that FSD performs better than the other interfaces (FSD-PSD: $p=0.04$; FSD-AD: $p=0.02$), whereas PSD and AD seem to have similar results (PSD-AD: $p=0.88$).

@@

\subsection{Learning}

@@

\section{Results on Musical Sounds}

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{gfx/analyse_music1.eps} 
\end{center}
\caption{\label{fig1Music} Average and standard deviation for (a) the total search durations, (b) the number of heard sounds and (c) the number of unique heard sounds.}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{gfx/analyse_music2.eps} 
\end{center}
\caption{\label{fig2Music} evolution of (a) the average search durations, (b) the average numbers of heard sounds, and (c) the average numbers of unique heard sounds at each target sound search. Lines are linear regression fits.}
\end{figure}

\gl{merge fig. 5 and 7}
% if space is need fig 1 could be merged

\subsection{Outliers}

\ref{fig1Music}

\subsection{Learning}

\ref{fig2Music}
